{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-27 wacv_for_review.tex
ECO, CCOT and SCT trackers added into the experiments
Results Text Updated based on the figures

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following functionality would make it more useful
in the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. Figure
\ref{fig:UAV123_DATASET} shows the results on the UAV123 dataset. {\it
  E}nKCF outperformed most of the high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about 5\% better than ours in accuracy, but 10-20 times
slower. For the scale adaptation, {\it E}nKCF did second best in terms
of AUC for the success rate plot. It outperformed other tracking
methods in high-speed by about $20\%$-$25\%$ in AUC. In addition, it
performed even better than those algorithms that are slow, but a
slightly better in precision. For example, for AUC, {\it E}nKCF
outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle large displacement of objects in successive frames due to object
and camera motion. Specifically, we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than MUSTER.

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry any
other sensors than a monocular camera. Instead of just manually being
flew for video recording, an unmanned air vehicle (UAV) equipped with
an object or feature following functionality would make it more useful
in the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high speed
tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast}
and ones in relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, 
CCOT \cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and CCOT trackers
originally uses deep convolutional features. For the sake of fair comparison, we employ fHoG
and color-naming features similar to our study. Figure \ref{fig:UAV123_DATASET} shows 
the results on the UAV123 dataset. {\it  E}nKCF outperformed most of the high-speed tracking methods by
$3\%$-$15\%$ at 20 pixels precision. Three algorithms, SAMF, DSST, and
Struck did about $5\%$ better than ours in accuracy, but 10-20 times
slower. The more recent trackers, ECO and CCOT, on the other hand, outperforms
{\it  E}nKCF by $15\%$ while running at 10-15 times slower speed. 
For the scale adaptation, {\it E}nKCF did fourth best in terms
of AUC for the success rate plot. It outperformed other high-speed trackers
 by about $20\%$-$25\%$ in AUC. In addition, it performed even better than some of the lower-speed trackers. 
For example, for AUC, {\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while running at more
than $10$ and $30$ times faster.

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. The relative performance of {\it E}nKCF 
is similar to the UAV123 dataset. In particular, it performed reasonably at approximating target scale. 
It was the fifth best and the second fastest tracking algorithm. Among the other high-speed trackers,
it delivers the highest precision and success rates. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker. Finally, the ECO, and CCOT achieve $15\%$-$20\%$ higher
precision and success rates than ours while operating at 10-20 times slower rates.

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle large displacement of objects in successive frames due to object
and camera motion. Specifically, we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Also, we can observe the sensitivity of 
the state-of-the-art lower speed trackers to the video frame rate b
y running them on this downsampled dataset. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
fourth in AUC while running about 10 to 100 times faster than the top three trackers.

In the lower frame rate scenarios (10 fps), the ECO and CCOT's precision rates drop about
$10\%$ worse than the original frame rate scenarios. We believe that this is an indicator of
how good of a performance we can expect from these trackers on low-end hardware. The projected
frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5 and $\simeq$0.3 by using our 
convention described in section~\ref{introduction}. In this case, it would be reasonable to expect these
trackers to perform drastically worse on such hardware whereas the {\it E}nKCF can still perform similarly
due to its real-time speed on a low-end hardware. Our observations are also supported by \cite{mueller2017context}
that evaluates the correlation filter-driven trackers at variable frame rates matching their operation rates.

\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\tiny\quad\textbf{UAV123$\_$10fps}\\
\includegraphics[width=3.32cm]{./figures/pr_uav123_10fps.eps}
\includegraphics[width=3.30cm]{./figures/sr_uav123_10fps.eps}\\
\end{tabular}
\caption{Comparison of a modified {\it E}nKCF's performance with those
  of the state-of-the-art tracking algorithms on the UAV123$\_$10fps
  dataset where the original UAV123 data was temporally downsampled.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
